% This is a template for use with the MSU Thesis class
% Version 3.6 2022/08/23
%
% Class options: 
%[PhD]	Doctor of Philosophy (default) 
%[DEd]	Doctor of Education
%[DMA]	Doctor of Musical Arts
%[DNP]	Doctor of Nursing Practice
%[MA]	Master of Arts
%[MS]	Master of Science
%[MAT]	Master of Arts for Teachers
%[MBA]	Master of Business Administration
%[MFA]	Master of Fine Arts
%[MIPS]	Master of International Planning Studies
%[MHRL]	Master of Human Resources and Labor Relations 
%[MMus]	Master of Music
%[MPH]	Master of Public Health
%[MPP]	Master of Public Policy
%[MSW]	Master of Social Work
%[MURP]	Master in Urban and Regional Planning 
%%
% Default is PhD
%
%
% This template has everything in the right order.
% Just add real content and you're done!
%
\documentclass[]{msu-thesis}
%
% for a prettier, but possibly non-compliant table of contents use the [mixedtoc] option
% for a plain table of contents use the [plaintoc] option
% for a horrendous looking, but possibly required table of contents, use the [boldtoc] option
%
% If you have large tables/figures that need to be in landscape mode, add the [lscape] option
%
% The class accepts 12pt, 11pt or 10pt font size options. 
% For Times New Roman as in this example document, use 12pt (default).
%
\usepackage{amsmath}
\usepackage{csquotes}
\usepackage{float}
\usepackage{hyperref}
% \usepackage[document]{ragged2e}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
%\usepackage{multirow,ragged2e}
%\usepackage{ragged2e}
\usepackage{tikz-cd}
\usepackage[final]{pdfpages}
\usepackage[
backend=biber,
style=numeric-comp,
sorting=none
]{biblatex}
\addbibresource{bibliography.bib}
% If you require per-chapter appendices add the [chapterapp] option
%
% If you require per-chapter bibliographies add the [chapterbib] option
%
% This is standard fontenc for pdflatex
% If you use LuaLaTeX or XeLaTeX you should replace this with the fontspec package
\usepackage[T1]{fontenc}
%
% If the thesis office requires Times, we'll give them Times
% You can experiment with other font packages here if you like.
% If you are using XeLaTeX or LuaLaTeX load  TeX Gyre Termes, Times or Times New Roman font with \setmainfont
\usepackage{newtxtext,newtxmath} 
%
% Load any extra packages here
%
% You must specify the title of your thesis, your name, the field of study (not department), and the year
\title{Resonance Compensation Studies at the FNAL Recycler Ring}
\author{Cristhian Gonzalez-Ortiz}
\fieldofstudy{Physics} % This should be in sentence case
\date{2024}

% If you want a dedication page, specify the text of the dedication here and uncomment the next command.
%
%\dedication{This thesis is dedicated to someone.}
%
\begin{document}

% All the stuff before your actual chapters is called the front matter
\frontmatter
% First make the title page
\maketitlepage

% if you have public abstract (optional) it should go here
%\begin{publicabstract}
% Public abstract goes here
%\end{publicabstract}

% Next make the regular abstract (obligatory)
\begin{abstract}
% Your abstract goes here.  Master's 1 page max. PhD 2 page max.
Circular accelerators, such as the ones in the Fermilab Accelerator Complex, are indispensable tools driving scientific discovery by propelling particles to high energies and high intensities. In the context of the Proton Improvement Plan II (PIP-II) at Fermilab, the Recycler Ring (RR) is confronted with the challenge of high-intensity operation. The space charge tune shifts at these intensities necessitate the mitigation of third-order resonances. By measuring the Resonance Driving Terms (RDTs) for each resonance line, their strengths and damaging effects can be quantified. 

The study is focused on the utilization of dedicated normal and skew sextupoles for the compensation of these resonance lines. By employing the response matrix method to measure the Resonance Driving Terms (RDTs) relative to the currents in these sextupoles, a methodical approach to simultaneously compensate individual and multiple third-order resonances has been developed and assessed. The assessment and verification incorporate mapping out beam losses through dynamic and static tune scans, along with the utilization of the Ion Profile Monitor (IPM) system for beam size measurements. 

Furthermore, optimization algorithms have been explored and incorporated into the resonance compensation scheme. Parallel, to the work done at Fermilab, the study extends its scope by performing related experiments at the CERN Proton Synchrotron Booster (PSB). For these experiments, multiple resonance lines in the tune diagram were compensated by optimizing the currents in the compensation elements with the aid of advanced optimization algorithms.  

High-intensity operation of the Recycler Ring involves understanding the interplay between the space charge tune spread, resonance lines, and specialized subsystems such as transverse dampers. The following study also delves into experiments that try to discern each of these phenomena, while highlighting challenges still ahead. Overall, these studies indicate the feasibility of compensating for multiple third-order resonances, contributing to the objectives of PIP-II for the reliable delivery of a 1.2 MW proton beam to experimental facilities.
\end{abstract}

% Force a newpage
\clearpage
% Make the copyright page. The Graduate School ridiculously claims that you
% can't have a copyright page unless you pay ProQuest to register the copyright.
% This is simply not the case, so put in your copyright page whether or not you
% intend to pay Proquest to register the copyright.
% Furthermore, they have occasionally complained that the copyright mark is aligned
% to the right, even though that has been the format for more than a decade.
% If they want the copyright mark aligned to the left, use \makecopyrightpage* instead. 

\makecopyrightpage 

% If you have a dedication page, uncomment the next command to print the dedication page
%
%\makededicationpage
%
\clearpage
% Your Acknowledgements are formatted like a chapter, but with no number
\chapter*{Acknowledgements}
\DoubleSpacing % Acknowledgements should be double spaced
I would like to acknowledge Dr. Robert Ainsworth for taking those couple of nutmegs when we played footy together. Thank you, Rob, for making me a better scientist and teaching me so many valuable life lessons. Thank you for always having my back.

I would like to acknowledge the instrumental role of Dr. Peter Ostroumov in these years of my Ph.D. at Michigan State University. Thank you, Peter, for pushing me to be a better physicist and scientist, every day. Thank you for believing in me, even in the moments I didn't believe in myself.

Thank you to the members of my doctoral committee, Steve Lund, Yue Hao, Paul Gueye and Kendall Mahn. I truly value every comment and every word of encouragement at all of our meetings. We did not meet frequently, but your guidance was crucial through this process. Also thank you to whole support network at MSU and FRIB---these are institutions where you will never feel alone and always have someone support you when needed.

I would like to acknowledge the whole MI/RR department at Fermilab. Thank you, Kyle, Adam, Nino, Osama, Betiay, Denton, Marty, Mike, Phil, MaryKate, Matilda and Meiqin, and whoever I might have left out. Thank you for having the patience and your unconditional support while I pushed through with my experiments. You guys always had a smile even when I asked the most basic questions. Special acknowledgement to the operations team at Fermilab for always being open to questions and discussion. Thank you for having the patience to withstand me when I would continuously trip the permit on beam losses. I would also like to acknowledge the hospitality and awesomeness of our CERN collaborators, specially Foteini and Tirsi. 

Luisa. Tú has sido el soporte y la inspiración estos últimos años para poder estar a puertas de cruzar la meta. Gracias por siempre estar ahí y no rendirte nunca con lo nuestro. Vamos a lograr grandes cosas juntos. Ya casi adoptamos un perrito, manguitos szah.

Gracias a toda mi familia, incluyendo a esos amigos que considero mi familia, por apoyarme en este camino. Desde Bogotá hasta llegar a Chicago pasando por Lansing. Nunca pensé en llegar tan lejos de la loma. No hubiera podido terminar este doctorado sin el apoyo de todos ustedes. Gracias por estar ahí en cada momento de mi vida. Thank you, Sjuju, the great celestial whale overseer.

%
\clearpage
% We need to turn single spacing back on for the contents/figures/tables lists
\SingleSpacing
\tableofcontents* % table of contents will not be listed in the TOC
%\clearpage
%\listoftables % comment this out if you have no tables
%\clearpage
%\listoffigures % comment this out if you have no figures
%
% If you have a Key to  Abbreviations/symbols you would add each abbreviation in its display order
% using as in the following examples:
\abbrev{MSU}{Michigan State University}
\abbrev{FNAL}{Fermilab National Accelerator Laboratory}
\abbrev{RR}{Recycler Ring}
\abbrev{MI}{Main Injector}
\abbrev{RDTs}{Resonance Driving Terms}
\abbrev{NuMI}{Neutrinos at the Main Injector}
\abbrev{PSB}{CERN Proton Synchrotron Booster}
\abbrev{ACNET}{Accelerator Control Network}
\abbrev{TbT}{Turn-by-Turn Data}
\abbrev{NAFF}{Numerical Analysis of Fundamental Frequencies}
\abbrev{GFCs}{Generating Function Coefficients}
% Then issue a \clearpage and print the list 
\clearpage
\listofabbreviations 
% Comment out the code above if you have no abbreviations
% See the documentation if you need to change the width or format of the abbreviation column

% See the class documentation and the Memoir manual for how to create other lists
%
% If you are using an algorithm formatting package (e.g. algorithmicx or algorithm2e)
% please read the class documentation carefully on how to use these packages with the class
% The class provides an {algorithm} environment and a \listofalgorithms by default 
%
\mainmatter
%
% The next line removes the dots in chapter headings in the TOC
% May violate thesis office rules
%\addtocontents{toc}{\protect\renewcommand{\protect\cftchapterdotsep} {\cftnodots}}

% ALL documents using this class must have \chapter divisions
% If you are using it for an MA/MS thesis you still need to have chapters, even if they are very small.
\include{chapter1}
\include{chapter2}
\include{chapter3}
\include{chapter4}
\include{chapter5}
\include{chapter6}
\include{chapter7}
\printbibliography
%\chapter{Your first chapter}
%
% If you have pages that must appear in landscape mode, use the [lscape] documentclass option
% and enclose the pages in a {landscape} environment.
%\clearpage\pagestyle{lscape} % first clear the page and change the pagestyle
%\begin{landscape}
%
% your landscape table(s) or figure(s) here
%
%\end{landscape}
%\pagestyle{plain} % remember to change the pagestyle back to plain
%
%
% Your bibliography command here 
% e.g. \bibliography{your-bib-file}) if using natbib
% e.g. \printbibliography if using biblatex
%
% Remember that although the bibliography is single spaced, there needs to
% be a blank line between entries. This is set by your bibliography package
% If you are using natbib it is \bibsep; if using biblatex it's \bibitemsep
% These are set automatically by the class if you are using these packages
%
% If you need per-chapter bibliographies, you need to use the [chapterbib]
% class option and you would use \makebibliographypage before each
% chapter level bibliography and then the relevant bibliography command
% You should not use the \backmatter command 
%
% If you have appendices, they would go here.  
% If you only have one appendix it will look like this: (comment this out if you have no appendices)
% \begin{appendices}
% \include{appendix1}
% \include{appendix2}
% \end{appendices}
%
%
% If you have more than one appendix, you need to use 
%   \begin{appendices}
%   \chapter{First appendix}
%   \chapter{Second appendix}
%   \end{appendices}
%
% If each chapter has its own set of appendices, then load the class with the [chapterapp] option
% and put your {appendix} or {appendices} environments at the end of each chapter.
%
%
% Even though it is very unintuitive, per-chapter appendices are STILL \chapter commands
% in your document!  If you use \section it will not work properly.
% 
% You should not use the \backmatter command 
\end{document}

